RAX: A porting complexity evaluation tool for RISC-V

### 2023-10-09 Paper/latex/paper.tex
Add figures.

\section{RAX}
The following is an introduction to the process of RAX construction.
During the analysis phase,architecture-related factors are obtained through the Commit tool for selection.
A scanning tool is built to get potential modification workload.
Finally,an appropriate machine learning model is selected as a classification.

@@

\subsubsection{Factor 1: Cyclomatic Complex(CC)}
RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in section 2.3.
This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy,we form a scoring interval in the range of $[0~5]$.
We then calculated the Spearman correlation coefficient and conducted significance analysis between score and the CC factors.
The Spearman coefficient is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
This indicates a significant correlation between the two variables.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as the picture shows:
Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.

@@

\section{Related Work}
The development of the RISC-V ecosystem is rapidly progressing.
In the realm of scientific computing, Tine Blaise et al. [9] accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al. [3] designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment.
Alvares et al. [11] proposed using the development team's "tolerance" for code complexity to infer team development capabilities and performance indicators for projects.
Vard et al. [12] emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.

>>>>

\section{RAX}
The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:flow-chart}.
During the analysis phase,architecture-related factors are obtained through the Commit tool for selection.
A scanning tool is built to get potential modification workload.
Finally,an appropriate machine learning model is selected as a classification.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{flow-chart.pdf}
  \caption{Flow chart for method to build RAX}
  \label{fig:flow-chart}
  \Description{Flow chart for method to build RAX}
\end{figure}

@@

\subsubsection{Factor 1: Cyclomatic Complex(CC)}
RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in section 2.3.
This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy,we form a scoring interval in the range of $[0~5]$.
We then calculated the Spearman correlation coefficient and conducted significance analysis between score and the CC factors.
The Spearman coefficient is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
This indicates a significant correlation between the two variables.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:relationship}.
Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{relationship.pdf}
  \caption{The relationship between score and CC}
  \label{fig:relationship}
  \Description{The relationship between score and CC}
\end{figure}

@@

\section{Related Work}
The development of the RISC-V ecosystem is rapidly progressing.
In the realm of scientific computing, Tine Blaise et al. [9] accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al. [3] designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment.
Alvares et al. [11] proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
Vard et al. [12] emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
